Local Adaptive Optimization of Time step

### 2013-10-06 report/report.tex
Initialized new simulation (atomic) and presentation of experiments

\title{Local Adaptive Optimization of Time step}
\author{Malte Stær Nissen\\University of Copenhagen\\\texttt{malte.nissen@gmail.com} \and Supervisor: Sune Darkner\\University of Copenhagen\\\texttt{darkner@diku.dk}}

@@

>>>>

\title{Local Adaptive Optimization of Time step}
\author{Malte Stær Nissen\\
        University of Copenhagen\\
        \texttt{malte.nissen@gmail.com} \and
        Supervisor: Sune Darkner\\University of Copenhagen\\\texttt{darkner@diku.dk}}

@@

\begin{align}
F_k &= -k \\
F_m &= -F
\end{align}
